A Formal Model of Checked C

### 2023-01-09 sandp23/formal.tex
Adding all

>>>>

In \lang, the type equability ($=_{\Theta}$) and subtype ($\sqsubseteq$) relations are given in \Cref{fig:checkc-subtype}.
We provide some example descriptions here.
Type equality $\tau=_{\Theta}\tau'$
is a type construct equivalent relation defined by the bound equality ($=_{\Theta}$) in (NT-)array pointer types
and the alpha equivalence of two function types;
i.e., two (NT-)array pointer types $\tallarrayb{\bvar}{\tau} $ and $ \tallarrayb{\bvar'}{\tau'}$ are equivalent, if 
$\bvar =_{\Theta} \bvar'$ and $\tau=_{\Theta}\tau'$; two function types 
$\tfun{\overline{x}}{\overline{\tau}}{\tau} $ and $ \tfun{\overline{y}}{\overline{\tau'}}{\tau'}$
are equivalent, if we can find a same length (as $\overline{x}$ and $\overline{y}$) variable list $\overline{z}$ that is substituted for $\overline{x}$ and $\overline{y}$ in $\overline{\tau} \to {\tau}$ and $\overline{\tau'} \to {\tau'}$, resp.,
and the substitution results are equal.
\aravind{For the above paragraph, give concrete example, For example: array is a subtype of ptr, etc}

\aravind{We should explain how our type checker restricts unsafe interactions between checked and tainted pointer types.}

\begin{minted}[xleftmargin=30pt, mathescape, escapeinside=||, fontsize=\footnotesize]{c}
a -> checked pointer
b -> Tainted pointer
c -> Unchecked pointer.

_Ptr<int> a;
_t_Ptr<int> b;
int *c;

a = b; // Not allowed.
b = a; // Not allowed.

a = (_Ptr<int>)c; // This is okay.
a = (_Ptr<int>)b; // Not allowed.
\end{minted}
